### 2020-01-18 nlp_models.tex
updating NLP section'

\paragraph{OpenAI GPT Models}
We use the \emph{WeightWatcher} tool to analyze the OpenAI GPT and GPT2 models, which gives us
the opportunity to analyze the effect of both training the same model with different size data sets,
and increasing sizes of both the data set and architectures.
These models have generated significant media attention because of their remarkable ability to
 generate fake text that appears to be real and the potential misuse of this.
For this reason, the original GPT model was trained on on a deficient data set, rendering
the model interesting but not fully functional.  Later, OpenAI released a much improved model--
GPT2 (small)--which has the same architecture and number of layers as GPT, but has
been trained on a larger and betterd data set (and with other changes), making it
remarkably good at generating (near) human-quality fake text.  
By comparing GPT and GPT2, we can indentify empirical markers indicating that
a model has been poorly trained and may perform poorly when deployed.

>>>>

\paragraph{OpenAI GPT Models}
We use the \emph{WeightWatcher} tool to analyze the OpenAI GPT and GPT2 models, which gives us
the opportunity to analyze the effect of both training the same model with different size data sets,
and increasing sizes of both the data set and architectures.
These models have generated significant media attention because of their remarkable ability to
 generate fake text that appears to be real and the potential misuse of this.
For this reason, the original GPT model was trained on on a deficient data set, rendering
the model interesting but not fully functional.  Later, OpenAI released a much improved model--
GPT2 (small)--which has the same architecture and number of layers as GPT, but has
been trained on a larger and better data set (and with other changes), making it
remarkably good at generating (near) human-quality fake text.  
By comparing the poorly trained GPT to the well trained GPT2, we
indentify empirical indidcators for when  model has in fact
been poorly trained and may perform poorly when deployed.
